---
title: "load_ibama"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

The dataset contains data related to environmental embargoes and fines at the individual
level from 2005 to the present day. The funtion downloads and compiles data on environmental fines at the municipality or state levels considering the Amazon region. The user has the option to either download
or load the previously stored raw data, choosing a time-location aggregation level.

The function returns a data frame with aggregates considering, for each
time-location period, counts for total the number of infractions, 
infractions that already went to trial, and 
number of unique perpetrators of infractions.

The user has the option of obtaining data either in Portuguese or in English.

# Usage:

```{r, eval = FALSE}

There are five parameters in this function:

  1. dataset = "areas_embargadas"
  
  2. raw_data : there are two options:
  # TRUE: if you want to visualize the raw data.
  # FALSE: if you want to visualize the processed version of the data. 
 
  3. geo_level: "municipality" or "state"
  
  4. language : you can choose between portuguese and english
  
  5. legal_amazon_only: setting the return of Legal Amazon Data (legal_amazon_only = TRUE) or Country´s Data (legal_amazon_only = FALSE)
  
```

# Examples:

```{r, eval = FALSE}
data = load_ibama(dataset = "areas_embargadas", raw_data = FALSE, 
                  geo_level = "municipality", language = "eng",
                  legal_amazon_only = FALSE)



```
load_ibama <- function(dataset = "areas_embargadas", raw_data = FALSE,
                       geo_level = "municipality",
                       language = "eng",
                       legal_amazon_only = FALSE){
